Measuring contrast processing in the visual system using SSVEP

### 2024-04-21 review.qmd
Minor edits

where ${R_{\mathrm{max}}}$ describes the maximum response level, $C_{\mathrm{in}}$ is the input contrast (or the time-varying waveform), $C_{50}$ is the 'semi-saturation constant' (the point at which the response is at half-maximum) and *n* controls the steepness of the curve.

@@

![Illustration of how a sinusoidal input signal is affected by a nonlinear transducer. The input wavefore (left panel) is frequency doubled by the squaring operator, and now features energy at the second harmonic (10Hz) and its multiple (middle panel). The contrast response function is now nonlinear, and saturates at high contrasts (right panel).](Figures/transducer.pdf){#fig-transducer}

>>>>

where ${R_{\mathrm{max}}}$ describes the maximum response level, $C_{\mathrm{in}}$ is the input contrast (or the time-varying waveform), $C_{50}$ is the 'semi-saturation constant' (the point at which the response is at half-maximum) and *n* controls the steepness of the curve (with a typical value around $n=2$.

@@

![Illustration of how a sinusoidal input signal is affected by a nonlinear transducer. The input wavefore (left panel) is frequency doubled by the squaring operator, and now features energy at the second harmonic (10Hz) and its multiple (middle panel). The contrast response function at the second harmonic is now nonlinear, and saturates at high contrasts (right panel).](Figures/transducer.pdf){#fig-transducer}
